---
title: "xgboost"
author: "A. Berg"
date: "10/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir ="C:/Users/Berg/Documents/R/ML_pred_CRC")
knitr::opts_knit$set(set.dir ="C:/Users/Berg/Documents/R/ML_pred_CRC")
knitr::opts_chunk$set(dev = "png",
                      dpi = 600,
                      echo = FALSE,
                      cache = TRUE,
                      warning= F, 
                      results='hide')


deps = c("tictoc","readr","readxl","knitr","rmarkdown","tidyverse","broom", "furrr", 
         "future.apply", "caret", "mikropml", "UpSetR", "cowplot", 
         "MLeval", "MicrobiotaProcess", "e1071", "RColorBrewer", "ampvis2", "dplyr", "stringr", "naivebayes", "writexl");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

```

#Load Data
```{r}
set.seed(42)
tic()
source("code/load_data.R") #2min
toc()

```




## Feature Selection
Evaluate the number of features necessary for RF to work:

```{r, Feature Selection}
tic()
source("code/XGB/xgb_feature_selection.R") #
toc()
xgb_feature_plot

```


## Hyperparameter tuning to final model
Tune the mtry parameter, the number of trees is predefined to 500
1) rough tune of 7, sqrt(183), 28 and 183
2) fine tune of 10-30, and a secon fine tune of the top 5 values 
3) final model with mtry =

all trains are repeated cross validation of 5-fold 10-CV in a seed loop of a 100
```{r, Hyperparameter tuning}

source("code/XGB/xgb_hptuning.R") 

xgb_tune_plot
```



## Internal Validation



```{r, Internal Validation}

source("code/XGB/xgb_internal_validation.R") 

xgb_internal_pred_stats[["table"]]

xgb_stats_int

xgb_histogram

```

####
## External Validation

```{r, External Validation}
#load data
source("code/load_externalvalidation_data.R") 

source("code/XGB/xgb_external_validation.R") 
```


## Robustness test: Other disease 

```{r, Robustness test: Other disease }
source("code/XGB/xgb_robust_disease.R") 


```


## Robustness test: Other sequencing method

```{r, Robustness test: Other sequencing method}
source("code/RF/rf_robust_seq.R") 


```



